Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-26 awipev-CO2.Rmd

# time series temp
ts_temp <- d %>%
  dplyr::filter(!is.na(temp_insitu_11m)) %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = temp_insitu_11m), col = "blue", size = 0.15) +
  labs(title = "", x = "", y = "Temp. 11 m (°C)") +
  mytheme(size_labs = 8)
print(ts_temp) 
# time series sal
ts_sal <- d %>%
  dplyr::filter(!is.na(sal_mix)) %>% 
ggplot() +
  geom_point(aes(x = datetime, y = sal_mix), col = "blue", size = 0.15) + 
  labs(title = "", x = "", y = "Salinity") +
  mytheme(size_labs = 8)
print(ts_sal) 
# time series pco2
ts_pco2 <- d %>%
  dplyr::filter(!is.na(pco2_corr)) %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = pco2_corr), col = "blue", size = 0.15) +
  scale_x_datetime(limits = xlim) +
  labs(title = "", x = "", y = expression(paste("pC", O[2], " (", mu, "atm)"))) +
  mytheme(size_labs = 8)
print(ts_pco2) 
# time series pH
ts_ph <- d %>%
  dplyr::select(datetime, pHint_tot_sf, ph_dur_corr) %>%
  dplyr::filter(!is.na(pHint_tot_sf)) %>%
  pivot_longer(-datetime, names_to = "pH", values_to = "value") %>%
  ggplot() +
  geom_point(aes(x = datetime, y = value, colour = pH), size = 0.15) +
  scale_x_datetime(limits = xlim) +
  labs(title = "",
       x = "",
       y = expression(paste("p", H[T]))) +
  # scale_color_manual(
  #   values = c("blue", "red"),
  #   name = "",
  #   breaks = c("pHint_tot_sf", "ph_dur_corr"),
  #   labels = c("SeaFET", "Durafet")
  # ) +
  annotate(
    geom = "text",
    x = as.POSIXct("2018-06-01"),
    y = 8.35,
    label = "seaFET",
    color = "blue", size = 2
  ) +
  annotate(
    geom = "text",
    x = as.POSIXct("2018-06-01"),
    y = 8.25,
    label = "Durafet",
    color = "red", size = 2
  ) +
  mytheme(size_labs = 8) +
  theme(legend.position = "none")
print(ts_ph) 
# time series AT
ts_at <- d %>%
  dplyr::filter(!is.na(at_calc)) %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = at_calc), col = "blue", size = 0.15) +
  scale_x_datetime(limits = xlim) +
  labs(title = "", x = "Time", y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
  mytheme(size_labs = 8) +
  theme(axis.title.x = element_text(face="plain", size=8))
print(ts_at) 
# time series Omega
ts_oa <- d %>%
  dplyr::filter(!is.na(oa)) %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = oa), col = "blue", size = 0.15) +
  scale_x_datetime(limits = xlim) +
  labs(title = "", x = "Time", y = expression(paste(Omega[a]))) +
  Mytheme(size_labs = 8) +
  theme(axis.title.x = element_text(face="plain", size=8))
print(ts_oa) 
#assemble time-series figure
cp <- cowplot::plot_grid(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, ts_oa,
                   align = "v",
                   #labels = "AUTO",
                   ncol = 1
                   #width = 18,
                   #units = "cm"
                   )
print(cp)
cowplot::ggsave2(filename = "figures/ts_gg.png", plot = cp, height = 20, units = "cm")

>>>>

# time series temp
ts_temp <- d %>%
  dplyr::filter(!is.na(temp_insitu_11m)) %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = temp_insitu_11m), col = "blue", size = 0.15) +
  labs(title = "", x = "", y = "Temp. 11 m (°C)") +
  mytheme(size_labs = 8)
# time series sal
ts_sal <- d %>%
  dplyr::filter(!is.na(sal_mix)) %>% 
ggplot() +
  geom_point(aes(x = datetime, y = sal_mix), col = "blue", size = 0.15) + 
  labs(title = "", x = "", y = "Salinity") +
  mytheme(size_labs = 8)
# time series pco2
ts_pco2 <- d %>%
  dplyr::filter(!is.na(pco2_corr)) %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = pco2_corr), col = "blue", size = 0.15) +
  scale_x_datetime(limits = xlim) +
  labs(title = "", x = "", y = expression(paste("pC", O[2], " (", mu, "atm)"))) +
  mytheme(size_labs = 8)
# time series pH
ts_ph <- d %>%
  dplyr::select(datetime, pHint_tot_sf, ph_dur_corr) %>%
  dplyr::filter(!is.na(pHint_tot_sf)) %>%
  pivot_longer(-datetime, names_to = "pH", values_to = "value") %>%
  ggplot() +
  geom_point(aes(x = datetime, y = value, colour = pH), size = 0.15) +
  scale_x_datetime(limits = xlim) +
  labs(title = "",
       x = "",
       y = expression(paste("p", H[T]))) +
  # scale_color_manual(
  #   values = c("blue", "red"),
  #   name = "",
  #   breaks = c("pHint_tot_sf", "ph_dur_corr"),
  #   labels = c("SeaFET", "Durafet")
  # ) +
  annotate(
    geom = "text",
    x = as.POSIXct("2018-06-01"),
    y = 8.35,
    label = "seaFET",
    color = "blue", size = 2
  ) +
  annotate(
    geom = "text",
    x = as.POSIXct("2018-06-01"),
    y = 8.25,
    label = "Durafet",
    color = "red", size = 2
  ) +
  mytheme(size_labs = 8) +
  theme(legend.position = "none")
# time series AT
ts_at <- d %>%
  dplyr::filter(!is.na(at_calc)) %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = at_calc), col = "blue", size = 0.15) +
  scale_x_datetime(limits = xlim) +
  labs(title = "", x = "Time", y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
  mytheme(size_labs = 8) +
  theme(axis.title.x = element_text(face="plain", size=8))
# time series Omega
ts_oa <- d %>%
  dplyr::filter(!is.na(oa)) %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = oa), col = "blue", size = 0.15) +
  scale_x_datetime(limits = xlim) +
  labs(title = "", x = "Time", y = expression(paste(Omega[a]))) +
  Mytheme(size_labs = 8) +
  theme(axis.title.x = element_text(face="plain", size=8))
#assemble time-series figure
cp <- cowplot::plot_grid(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, ts_oa,
                   align = "v",
                   #labels = "AUTO",
                   ncol = 1
                   #width = 18,
                   #units = "cm"
                   )
cowplot::ggsave2(filename = "figures/ts_gg.png", plot = cp, height = 20, units = "cm")
